Notes on Validated Model Counting \\ Version of \today

### 2022-09-16 doc/mc-notes.tex
Minor tweaks

\begin{figure}
\begin{verbatim}
c Node P5 = AND(var-3, var-4)
12 p 5 3 4 0
c Node P6 = AND(-var-3, -var-4)
15 p 6 -3 -4 0
c Node S7 = OR(P5, P6)
18 s 7 5 6 13 16 0
c Node P9 = AND(var-1, -var-2, S7)
21 p 9 1 -2 7 0
c Node P10 = AND(-var-1, S7)
25 p 10 -1 7 0
c Node S11 = OR(P9, P10)
28 s 11 9 10 22 26 0
\end{verbatim}
\caption{Declarations of operations to represent Formula \#4}
\label{fig:eg4:ops}
\end{figure}

>>>>

\begin{figure}
\begin{verbatim}
c P5 = AND(x-3, x-4)
12 p 5 3 4 0
c P6 = AND(-x-3, -x-4)
15 p 6 -3 -4 0
c S7 = OR(P5, P6)
18 s 7 5 6 13 16 0
c P9 = AND(x-1, -x-2, S7)
21 p 9 1 -2 7 0
c P10 = AND(-x-1, S7)
25 p 10 -1 7 0
c S11 = OR(P9, P10)
28 s 11 9 10 22 26 0
\end{verbatim}
\caption{Declarations of operations to represent Formula \#4}
\label{fig:eg4:ops}
\end{figure}
